Compare different versions of BM 36 from MSSM

### 2016-11-04 code/Rmd/BM36_Compare_All_Data.Rmd
Minor changes

@@

tmp = rbind(data.frame(Comp = 'Portal_vs_BAM', values = diag(cr.por.bam)),
            data.frame(Comp = 'Portal_vs_FASTQ', values = diag(cr.por.fastq)),
            data.frame(Comp = 'Portal_vs_synBAM', values = diag(cr.por.synbam)),
            data.frame(Comp = 'FASTQ_vs_synBAM', values = diag(cr.fastq.synbam)),
            data.frame(Comp = 'FASTQ_vs_BAM', values = diag(cr.fastq.bam)))
p = ggplot(tmp, aes(x = Comp, y = values)) + geom_boxplot()
p = p + ylab('Correlation') + xlab('')
p
```

>>>>

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)

@@

tmp = rbind(data.frame(Comp = 'Portal_vs_BAM', values = diag(cr.por.bam)),
            data.frame(Comp = 'Portal_vs_FASTQ', values = diag(cr.por.fastq)),
            data.frame(Comp = 'Portal_vs_synBAM', values = diag(cr.por.synbam)),
            data.frame(Comp = 'FASTQ_vs_synBAM', values = diag(cr.fastq.synbam)),
            data.frame(Comp = 'FASTQ_vs_BAM', values = diag(cr.fastq.bam)))
p = ggplot(tmp, aes(x = Comp, y = values)) + geom_boxplot()
p = p + ylab('Correlation') + xlab('')
p

plot(diag(cr.fastq.synbam), diag(cr.fastq.bam), xlab = 'FASTQ_vs_synBAM', ylab = 'FASTQ_vs_BAM')
```
